---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Main Idea

The main idea of `{datacutr}` is to provide a standardized approach to applying a datacut to SDTM datasets.  
The process applied by the package is the following,  
* create a meta dataset `DCUT` that references all patients to be included within the cut, and the cut date to be used as reference (normally the Clinical Cut-off Date that data has been cleaned to).  
* using `DCUT` as reference, records can be removed from the SDTM data that are either a) patients not part of the reference `DCUT`, or b) records that can be identified as after the data cut date supplied.  

The package relies on creating lists of SDTM to be processed in specific ways, these include,  
* No cut - SDTM to remain exactly as source
* Patient cut - Only Patients identified in source meta `DCUT` are kept, no other exclusion of records is conducted  
* Date cut - Only Patients identified in source meta `DCUT` are kept, and records identified after the data cut date are removed  
* Special DM cut - As `DM` contains critical temporal derivations around Deaths that would require update within a data cut, this option allows the user to revert `DM.DTHFL` and `DM.DTHDTC` if death is identified after the data cut date

## Load Packages and Example Datasets

First, we will load our packages and example datasets. 

```{r, message=FALSE, warning=FALSE}
# Load packages

```

# Validation

All functions are reviewed and tested to ensure that they work as described in
the documentation. They are **not validated** yet.

# Starting a Script

`{datacutr}` provides a template R scripts as a starting point. See specific vignette pages for more details.

# Support

Support is provided via the `{datacutr}` Slack channel (link to be added).

# See also

- [Template scripts](https://github.com/pharmaverse/datacutr/tree/main/inst/templates)

- [Programming Strategy](programming_strategy.html)
