---
title: "Data Cut Read-out File"
date: "`r format(Sys.time(), '%c')`"
output: 
  html_document:
    df_print: paged
    toc: no
    toc_depth: '3'
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r tabulate function, include=FALSE}
library(reactable)
library(tibble)

# Overall Summary of Datacut Tab####
data_review <- function(pt_data, dt_data, dm_data, no_cut) {
  cyc_num <- 1
  sum_t <- tibble::tibble(
    Dataset = character(),
    `Cut Applied` = character(),
    `Before Cut` = numeric(),
    `After Cut` = numeric(),
    `Removed` = numeric(),
    `Modified` = numeric()
  )
  objects <- list(pt_data, dt_data, dm_data, no_cut)
  is_all_null <- all(sapply(objects, is.null))
  if (is_all_null) {
    cat("No data has been inputted into the read-out function.", " \n",
      "If you would like to view a summary of the datacut, please double check you have filled in
      all the parameters in the read_out() function (or process_cut() when using the wrapped
      approach.)", " \n",
      fill = TRUE
    )
  }
  # Patient Cut Data
  for (df in pt_data) {
    name <- names(pt_data)[cyc_num]
    x <- length(which(df$DCUT_TEMP_REMOVE == "Y"))
    uncut <- nrow(df)
    cut <- length(which(is.na(df$DCUT_TEMP_REMOVE)))
    sum_t <- add_row(sum_t,
      Dataset = toupper(name),
      `Cut Applied` = "PATIENT",
      `Before Cut` = uncut,
      `After Cut` = cut,
      `Removed` = x,
      `Modified` = NA
    )
    cyc_num <- cyc_num + 1
  }
  # Date Cut Data
  cyc_num <- 1
  for (df in dt_data) {
    name <- names(dt_data)[cyc_num]
    x <- length(which(df$DCUT_TEMP_REMOVE == "Y"))
    uncut <- nrow(df)
    cut <- length(which(is.na(df$DCUT_TEMP_REMOVE)))
    sum_t <- add_row(sum_t,
      Dataset = toupper(name),
      `Cut Applied` = "DATE",
      `Before Cut` = uncut,
      `After Cut` = cut,
      `Removed` = x,
      `Modified` = NA
    )
    cyc_num <- cyc_num + 1
  }
  # Uncut Data
  cyc_num <- 1
  for (df in no_cut) {
    name <- names(no_cut)[cyc_num]
    uncut <- nrow(df)
    sum_t <- add_row(sum_t,
      Dataset = toupper(name),
      `Cut Applied` = "NO CUT",
      `Before Cut` = uncut,
      `After Cut` = uncut,
      `Removed` = NA,
      `Modified` = NA
    )
    cyc_num <- cyc_num + 1
  }
  # DM Cut Data
  if (!is.null(dm_data)) {
    x <- length(which(dm_data$DCUT_TEMP_REMOVE == "Y"))
    y <- length(which(dm_data$DCUT_TEMP_DTHCHANGE == "Y"))
    uncut <- nrow(dm_data)
    cut <- length(which(is.na(dm_data$DCUT_TEMP_REMOVE)))
    sum_t <- add_row(sum_t,
      Dataset = "DM",
      `Cut Applied` = "DM",
      `Before Cut` = uncut,
      `After Cut` = cut,
      `Removed` = x,
      `Modified` = y
    )
  }
  # Custom table container
  sketch <- htmltools::withTags(table(
    class = "display",
    thead(
      tr(
        th(rowspan = 2, "Dataset"),
        th(rowspan = 2, "Cut Applied"),
        th(colspan = 4, "Total Number of Records")
      ),
      tr(
        lapply(names(sum_t)[-c(1, 2)], th)
      )
    )
  ))
  reactable(sum_t,
    columnGroups = list(
      colGroup("Total Number of Records",
        columns = c("Before Cut", "After Cut", "Removed", "Modified")
      )
    ),
    bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
    showPageSizeOptions = TRUE, striped = TRUE, showSortable = TRUE
  )
}

# Create tabs in the html ####
df_tabs <- function(data) {
  cyc_num <- 1
  # case when data = NULL
  if (is.null(data)) {
    return(cat("NO DATA TO VIEW"))
  } else {
    # include modified records in special dm cut
    if (exists("DCUT_TEMP_DTHCHANGE", where = data)) {
      cat("####", "DM", " \n")
      x <- length(which(data$DCUT_TEMP_REMOVE == "Y"))
      cat(paste("Number of records removed in DM: ", x, " \n"))
      y <- length(which(data$DCUT_TEMP_DTHCHANGE == "Y"))
      cat(paste("Number of records modified in DM: ", y, " \n", " \n"))
      removed <- data %>% filter(data$DCUT_TEMP_REMOVE == "Y" | data$DCUT_TEMP_DTHCHANGE == "Y")
      print(htmltools::tagList(reactable(removed,
        rowStyle = function(index) {
          row <- removed[index, ]
          if (!is.na(row$DCUT_TEMP_REMOVE)) {
            list(background = "#FFDFDF")
          } else if (!is.na(row$DCUT_TEMP_DTHCHANGE)) {
            list(background = "#DFF3FF")
          } else {
            NULL
          }
        },
        bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
        showPageSizeOptions = TRUE, striped = TRUE, wrap = FALSE, resizable = TRUE,
        showSortable = TRUE
      )))

      cat(" \n\n")
    } else {
      # table for each df in the datacut
      for (df in data) {
        name <- names(data)[cyc_num]
        cat("####", toupper(name), " \n")
        x <- length(which(df$DCUT_TEMP_REMOVE == "Y"))
        cat(paste("Number of records removed in ", toupper(name), ": ", x, " \n", " \n"))
        removed <- df %>% filter(df$DCUT_TEMP_REMOVE == "Y")
        print(htmltools::tagList(reactable(removed,
          bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
          showPageSizeOptions = TRUE, showSortable = TRUE,
          striped = TRUE, wrap = FALSE, resizable = TRUE
        )))
        cat(" \n\n")
        cyc_num <- cyc_num + 1
      }
    }
  }
}

# Summary Tab for each cut
sum_test <- function(data) {
  cyc_num <- 1
  cat("####", "Summary", " \n")
  sum_t <- tibble::tibble(
    Dataset = character(),
    `Before Cut` = numeric(),
    `After Cut` = numeric(),
    `Removed` = numeric()
  )
  # case when data = NULL
  if (is.null(data)) {
    cat("No data has been cut with this cut type.", " \n")
    cat("If you would like to apply this cut, please double check you have ran this cut / filled in
        all the parameters in process_cut() - for the wrapped approach - or read_out() - modular
        approach.")
    cat(" \n\n")
  } else {
    # DM-specific Summary Tab
    if (exists("DCUT_TEMP_DTHCHANGE", where = data)) {
      x <- length(which(data$DCUT_TEMP_REMOVE == "Y"))
      y <- length(which(data$DCUT_TEMP_DTHCHANGE == "Y"))
      uncut <- nrow(data)
      cut <- length(which(is.na(data$DCUT_TEMP_REMOVE)))
      sum_t <- tibble(
        Dataset = character(),
        `Before Cut` = numeric(),
        `After Cut` = numeric(),
        Removed = numeric(),
        Modified = numeric()
      ) %>%
        add_row(Dataset = "DM", `Before Cut` = uncut, `After Cut` = cut, Removed = x, Modified = y)
      print(htmltools::tagList(reactable(sum_t,
        columnGroups = list(
          colGroup("Total Number of Records",
            columns = c("Before Cut", "After Cut", "Removed", "Modified")
          )
        ),
        bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
        showPageSizeOptions = TRUE, striped = TRUE, showSortable = TRUE
      )))
      cat(" \n\n")
    } else {
      # Summary tabs for other cuts
      for (df in data) {
        name <- names(data)[cyc_num]
        x <- length(which(df$DCUT_TEMP_REMOVE == "Y"))
        uncut <- nrow(df)
        cut <- length(which(is.na(df$DCUT_TEMP_REMOVE)))
        sum_t <- add_row(sum_t,
          Dataset = toupper(name),
          `Before Cut` = uncut,
          `After Cut` = cut,
          `Removed` = x
        )
        cat(" \n\n")
        cyc_num <- cyc_num + 1
      }
      reactable(sum_t,
        columnGroups = list(
          colGroup("Total Number of Records", columns = c("Before Cut", "After Cut", "Removed"))
        ),
        bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
        showPageSizeOptions = TRUE, striped = TRUE, showSortable = TRUE
      )
    }
  }
}
```

### Details

This is an {datacur} auto-generated read-out file. It contains a summary of the changes made to the data after the cut has been applied.

The **Summary** tab outlines the datasets affected and what type of cut has been applied to each. 

You can investigate each of the types of cuts applied and look at the records removed and/or modified by looking at the **Datacut Dataset (DCUT)**, **Patient Cut**, **Date Cut** and **Special DM Cut** tabs. 

---

# {.tabset}

## Summary

### Summary of Datacut

---

```{r Review, results='asis', echo = FALSE}
data_review(patient_cut_data, date_cut_data, dm_cut, no_cut_list)
```

## Datacut Dataset (DCUT)

### DCUT dataset:

After filtering the input DS dataset (based on the given filter condition), any records where the SDTMv date/time variable is on or before the datacut date/time (after imputations) will be returned in the output datacut dataset (DCUT).

---

###
```{r dcut, echo = FALSE}
if (is.null(dcut)) {
  return(cat("NO DATA TO VIEW"))
} else {
  reactable(dcut,
    bordered = TRUE, filterable = TRUE, searchable = TRUE, pagination = TRUE,
    showPageSizeOptions = TRUE, striped = TRUE, showSortable = TRUE
  )
}
```

## Patient Cut 

### Patient Cut Datasets 

Patient cut to an SDTMv dataset (i.e. subset SDTMv observations on patients included in the dataset_cut input dataset).

Input dataset plus a flag `DCUT_TEMP_REMOVE` to indicate observations dropped when a patient level datacut is applied.

---

### {.tabset}
```{r, results='asis', echo = FALSE}
sum_test(patient_cut_data)
df_tabs(patient_cut_data)
```


## Date Cut 

### Date Cut Datasets

xxSTDTC or xxDTC Cut

Use to apply a datacut to either an xxSTDTC or xxDTC SDTM date variable. 
The datacut date from the datacut dataset is merged on to the input SDTMv dataset and renamed to `DCUT_TEMP_DCUTDTM`.

The flag `DCUT_TEMP_REMOVE` is added to the dataset to indicate observations removed when the cut is applied.

Note that this function applies a patient level datacut at the same time (using the `pt_cut()` function), and also imputes dates in the specified SDTMv dataset (using the `impute_sdtm()` function).

---

### {.tabset}
```{r, results='asis', echo = FALSE}
sum_test(date_cut_data)
df_tabs(date_cut_data)
```

## Special DM Cut 

### Special DM cut dataset

Special DM Cut to reset Death variable information past cut date

Applies patient cut if patient not in source DCUT, as well as clearing death information within DM if death occurred after datacut date.

Input dataset plus a flag `DCUT_TEMP_REMOVE` to indicate which observations would be dropped when the datacut is applied, and a flag `DCUT_TEMP_DTHCHANGE` to indicate which observations have death occurring after data cut date for clearing.

***For ease of interpretation, the records where death dates have been modified are flagged*** <span style="color: blue;">***BLUE.***

***The records where records have been removed are flagged*** <span style="color: red;">***RED.***

---

### {.tabset}
```{r dm_cut, results='asis', echo = FALSE}
sum_test(dm_cut)
df_tabs(dm_cut)
```

